---
title: "Small Tasks"
author: "Aarsh Batra"
date:  "2021/11/19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# note: using load_all and document() within the rmd file is 
# crucial as loading it outside the context of the rmd file 
# (for example in the console) will not give it access to the 
# functions that are stored in the R sub-directory.

devtools::load_all()
devtools::document()

```

```{r libraries, include=FALSE}
library(tidyverse)
library(roxygen2)
library(envnames)
library(tidyr)
library(magrittr)
library(ggplot2)
library(stringr)
library(skimr)
library(purrr)
library(forcats)
library(foreign)
library(haven)
library(dplyr)
library(broom)
library(glue)
library(VIM)
library(outliers)
library(ggplot2)
library(scales)
library(grid)
library(RColorBrewer)
library(psych)
library(lubridate)
library(janitor)
library(tidyselect)
```

## Document Structure

* This document is a single reference source for all small R data tasks (and their corresponding report generation).
 
* The task that is marked  **Active** is the current task at hand.
 
* The tasks that is marked **Inactive** (written in front of it) means that they were completed at some point but now lay dormant and can be reactivated later if needed. The code chunks for these tasks will remain inactive until they are reactivated. 

<hr>

### Task 1 (Inactive chunk): Filter data for the names in the [PUC Order](https://drive.google.com/file/d/1NWQHUx85j_rCRd1qZHzHEf08FgTP-7mg/view?usp=sharing).


## Read Raw Data




```{r PUCOrderFilterData-read-data, eval=FALSE, include=FALSE}
pucc_data_raw <- readr::read_csv("data-raw/PUCC Checking by CDVs in Petrol Pumps.csv")
```

## Clean raw data

```{r clean-raw-data, eval=FALSE, include=FALSE}

## cleaning steps (in order as they are performed)
# 1. clean column names
# 2. create a "date_only" column from timestamp column
# 3. create a "time_only" column (24 hr format) from timestamp column
# 4. convert "civil_defence_volunteer_name" column to lowercase
# 5. convert "petrol_pump_location" column to lowercase
# 6. coerce "vehicle_category", "vehicle_pucc_valid"
#    , "civil_defence_volunteer_name" columns to class "factor"

pucc_data_cleaned <- pucc_data_raw %>%
  janitor::clean_names() %>%
  dplyr::mutate(date_only = lubridate::date(timestamp), 
                time_only = readr::parse_time(stringr::str_extract(timestamp, "(.:..:.. ..)| (..:..:.. ..)")), civil_defence_volunteer_name = stringr::str_to_lower(civil_defence_volunteer_name), 
                petrol_pump_location = stringr::str_to_lower(petrol_pump_location), 
                vehicle_category = haven::as_factor(vehicle_category), 
                vehicle_pucc_valid = haven::as_factor(vehicle_pucc_valid), 
                civil_defence_volunteer_name = haven::as_factor(civil_defence_volunteer_name)) %>%
  dplyr::select(timestamp, date_only, time_only, tidyselect::everything())

```


```{r task1-PUCOrderFilterData-cleaning-data, eval=FALSE, include=FALSE}


## Enter Nodal officers names list mentioned in the PUC Order PDF above
name_list <- c("nikhil", "yogesh kumar", "keshav", "dusyant yadav", 
               "saju p sharma", "kuldeep garg", "sunil kumar", 
               "yogesh", "jagdish jumar", "avinash", "angad pratab singh", 
               "rishikesh", "sunil sani", "vishal goel", "utkresh", "manish", 
               "girish chandra", "ram tirath yadav", "rajesh kumar", 
               "sagar dhiman", "guru shran mishra", "vikes solanki", 
               "mukesh kumar", "ajit singh", "robin ranjan", 
               "sunil kumar", "sachin sharan", "vishal rana", 
               "naresh", "jag mohan")

## enter date range for filtering PUC data

lower_limit_date <- c("2021-11-15")
upper_limit_date <- c("2021-11-19") 

date_range <- lubridate::as_date(lubridate::ymd(lower_limit_date) : lubridate::ymd(upper_limit_date))

## filtered_dataset
pucc_data_filtered <- pucc_data_cleaned %>%
  dplyr::filter(date_only  %in% date_range) %>%
  dplyr::filter(civil_defence_volunteer_name %in% name_list)

## save puc filtered dataset

# enter other (other than date) filters used to be used to create the name 
# of the file to be exported.

filters_other <- c("namelist")

file_name <- str_c("pucc_data", lower_limit_date, "to", upper_limit_date, filters_other, ".csv", sep = "_")

file_name <- str_c("smallTasksRmdScriptOutputFiles", file_name, sep = "/")

readr::write_csv(pucc_data_filtered, file_name)

```






## Task 2: Ad hoc task from transport department: Analyze a few data files and create graphs


# get data

```{r }

```


# Graph 1: Total number of registered vehicles in Delhi

```{r plot1-num-reg-veh}

# setting options for removing scientific notation from plots
options(scipen = 999)

reg_veh_tibble <- tibble(vehicle_type = c("Diesel", "Petrol", "Electric", "CNG", "Hybrid(Petrol/CNG)"), num_registered_vehicles = c(986007, 11055357, 123239, 
278236, 744089))

reg_veh_tibble$vehicle_type <- as.factor(reg_veh_tibble$vehicle_type)

plot1_num_registered_vehicles <- ggplot(reg_veh_tibble, mapping = aes(x = fct_reorder(vehicle_type, num_registered_vehicles), y = num_registered_vehicles)) + 
  geom_col(fill = "burlywood1", width = 0.6) +
  scale_y_continuous(breaks = seq(0, 12000000, 500000)) +
  geom_text(mapping = aes(label = num_registered_vehicles), position=position_dodge(width=0.9), vjust=-0.25) +
  labs(x = "Type of Vehicle", y = "Number of Registered Vehicles") +
  ggtitle("Number of Registered Vehicles") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggthemes::theme_tufte()

plot1_num_registered_vehicles

# ggsave(filename = "graph_num_registered_vehicles.jpeg")



```



## Graph 2: PUCC Challans Issued

```{r plot2-pucc-challan-issued}

# Assumptions:
# Given the document, I assume that the number of issuing places for DTC buses are different from the Petrol Pumps and Service Stations. 


# create tibble
pucc_challan_issued_tibble <- tibble(time_period = c("January 2021 to October 2021", "October 2021"), num_pucc_challans_issued = c(15678, 9522))

plot2_num_pucc_challans_issued <- ggplot(pucc_challan_issued_tibble, mapping = aes(x = time_period, y = num_pucc_challans_issued)) + 
  geom_col(fill = "burlywood1", width = 0.6) +
  scale_y_continuous(breaks = seq(0, 18000, 5000)) +
  geom_text(mapping = aes(label = num_pucc_challans_issued), position=position_dodge(width=0.9), vjust=-0.25) +
  labs(x = "Time Period", y = "Number of PUCC Challans Issued") +
  ggtitle("Number of PUCC Challans Issued") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggthemes::theme_tufte()

plot2_num_pucc_challans_issued

# ggsave("plot2_num_pucc_challans_issued.jpeg")

```

# Graph 3: Number of PUCC Issuing places

```{r plot3-pucc-issuing-places}
pucc_issuing_places <- tibble(places = c("Petrol Pumps", "Service Stations", "PUC for buses (DTC)"), number_of_places  = c(360, 300, 39))

plot3_num_pucc_issuing_places <- ggplot(pucc_issuing_places, mapping = aes(x = fct_reorder(places, number_of_places), y = number_of_places)) + 
  geom_col(fill = "burlywood1", width = 0.6) +
  scale_y_continuous(breaks = seq(0, 400, 50)) +
  geom_text(mapping = aes(label = number_of_places), position=position_dodge(width=0.9), vjust=-0.25) +
  labs(x = "PUCC Issuing Place", y = "Total Count") +
  ggtitle("Number of PUCC Issuing Places") +
  
  theme(plot.title = element_text(hjust = 0.5)) +
  ggthemes::theme_tufte()

plot3_num_pucc_issuing_places

# ggsave("plot3_num_pucc_issuing_places.jpeg")

```

# Graph 4: PUCC Certificates Issued

```{r}
# create tibble

months_modify <- c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul",
                   "Aug", "Sep", "Oct", "Nov(till Nov 21)")

pucc_certificates_issued_tibble <- tibble(time_period = months_modify , num_pucc_certificates_issued = c(490958, 449831, 499382, 260688, 176298, 480229, 371998, 340951, 544186, 805249, 509406))

plot4_updated_num_pucc_certificates_issued <- ggplot(pucc_certificates_issued_tibble, mapping = aes(x = fct_reorder(time_period, num_pucc_certificates_issued),  y = num_pucc_certificates_issued)) + 
  geom_col(fill = "burlywood1", width = 0.6) +
  scale_y_continuous(breaks = seq(0, 700000, 50000)) +
  geom_text(mapping = aes(label = num_pucc_certificates_issued), position = position_dodge(width=0.9), vjust=-0.25) +
  scale_x_discrete(limits = months_modify) +
  labs(x = "Time Period (2021)", y = "Number of PUCC Certificates Issued") +
  ggtitle("Number of PUCC Certificates Issued") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggthemes::theme_tufte()

 plot4_updated_num_pucc_certificates_issued

ggsave("plot4_updated_num_pucc_certificates_issued.jpeg")

```


# Graph 5: Number of Vehicles Impounded

```{r}

dat_impounding <- readxl::read_xlsx("data-raw/smallTasksRmdScript-Task(CreateGraphsTDNov252021)/impoundingVehicles.xlsx")

colnames(dat_impounding) <- c("time_period", "impounded_vehicle_10_year_old", "impounded_vehicle_15_year_old", "total_vehicles_impounded")

dat_impounding

dat_impounding <- dat_impounding %>%
  select(time_period, impounded_vehicle_10_year_old, impounded_vehicle_15_year_old) %>%
  mutate(time_period = month.name[1:11])


dat_impounding_clean <- pivot_longer(dat_impounding, cols = !time_period, names_to = "Impounded_Vehicle_Type", values_to = "count")

plot5_number_of_vehicles_impounded <-  ggplot(dat_impounding_clean, mapping = aes(x = fct_reorder(time_period, count), y = count)) +
  geom_col(mapping = aes(x = fct_reorder(time_period, count), y = count, fill = Impounded_Vehicle_Type), position = "dodge") + 
  scale_y_continuous(breaks = seq(0, 350, 50)) +
  labs(x = "Time Period (2021)", y = "Number of Vehicles Impounded") +
  ggtitle("Number of Vehicles Impounded") +
  scale_x_discrete(limits = month.name[1:11]) +
  theme(plot.title = element_text(hjust = 0.5)) +
  coord_flip() +
  ggthemes::theme_tufte()



ggsave("plot5_number_of_vehicles_impounded.jpeg")
  

# plot5_number_of_vehicles_impounded
```


# Graph 6: Actions taken against PCC's 3 months summary (September 1, 2021 to November 20, 2021)

```{r actions-taken}

actions_taken_summary_tibble <- tibble(action_type = c("Total PCC's", "SCN Issued", 
                                        "PCC Warnings", "PCC Suspended", 
                                        "PCC Cancelled"), 
                        total = c(972, 61, 107, 10, 6))

plot6_actions_taken_summary <- ggplot(actions_taken_summary_tibble, mapping = aes(x = fct_reorder(action_type, total), y = total)) + 
  geom_col(fill = "burlywood1", width = 0.6) +
  scale_y_continuous(breaks = seq(0, 1000, 50)) +
  geom_text(mapping = aes(label = total), position = position_dodge(width=0.9), vjust=-0.25) +
  labs(x = "Actions Taken", y = "Total") +
  ggtitle("Actions taken against PCC's 3 months Summary: Sep 1, 2021 to Nov 20, 2021") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggthemes::theme_tufte()


ggsave("plot6_actions_taken_summary.jpeg")

# plot6_actions_taken_summary

```


## Graph 7: Prosecution Report PUCC

```{r}
dat_prosecution <- readxl::read_xlsx("data-raw/smallTasksRmdScript-Task(CreateGraphsTDNov252021)/prosecution_report_pucc.xlsx")

dat_prosecution$period <- month.name[1:11]
  
dat_prosecution

plot7_prosecution_report_pucc <- ggplot(dat_prosecution, mapping = aes(x = period, y = num_challans_issued)) + 
  geom_col(fill = "burlywood1", width = 0.6) +
  scale_y_continuous(breaks = seq(0, 500, 10000)) +
  geom_text(mapping = aes(label = num_challans_issued), position = position_dodge(width=0.9), vjust=-0.25) +
  labs(x = "Time Period(2021)", y = "Number of Challans Issued") +
  ggtitle("Number of Challans Issued (with special drive at petrol pumps from Oct 21-28, 2021)") +
  scale_x_discrete(limits = month.name[1:11]) +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggthemes::theme_tufte()


plot_bar_transp_dept_format_data(dat_prosecution, "period", "num_challans_issued", "burlywood1", seq(0, 10000, 500), "foo", "foo1", "Title")


# plot7_prosecution_report_pucc

ggsave("plot7_prosecution_report_pucc.jpeg")

```



```{r}

cng_buses_delhi_tibble <- tibble(auth_name = c("DTC", "DIMTS/Cluster Buses"),
                           num_buses = c(3760, 3033))

plot8_cng_buses_in_delhi <- ggplot(cng_buses_delhi_tibble, mapping = aes(x = auth_name, y = num_buses)) + 
  geom_col(fill = "burlywood1", width = 0.6) +
  scale_y_continuous(breaks = seq(0, 5000, 1000)) +
  geom_text(mapping = aes(label = num_buses), position = position_dodge(width=0.9), vjust=-0.25) +
  labs(x = "Authority Name", y = "Number of CNG Buses") +
  ggtitle("Number of CNG buses currently running in Delhi") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggthemes::theme_tufte()

# plot8_cng_buses_in_delhi

ggsave("plot_8_cng_buses_delhi.jpeg")


```


```{r}

dat_gwr_daily_report <- readxl::read_xlsx("data-raw/smallTasksRmdScript-Task(CreateGraphsTDNov252021)/Dailyreport of Greenwar room softcopy.xlsx")


dat_gwr_daily_report$action_taken_on <- c("Vehicles(>10-15 yrs old)", "Trucks Non Essential Goods", 
                                    "Vehicles(>10-15 yrs old)", "Visible Poll Veh without PUCC")

dat_gwr_daily_report
plot9_dat_gwr_daily_report <- ggplot(dat_gwr_daily_report, mapping = aes(x = action_taken_on, y = log10(Total))) + 
  geom_col(mapping = aes(fill = type_of_action), width = 0.6, position = "dodge") +
  labs(x = "Actions Taken On", y = "total (log scale)") +
  ggtitle("Green War Room action report (November 17, 2021 to November 23, 2021)") +
  theme(plot.title = element_text(hjust = 0.5)) + 
  ggthemes::theme_tufte()

dat_gwr_daily_report

plot9_dat_gwr_daily_report

# ggsave("plot9_log_scale_dat_gwr_daily_report.jpeg")
```



## Task 3: Connect R to PostgreSQL.

# Steps completed: 
#  Successfully created an empty table in PostgreSQL.
#  From an excel file, imported some data into the empty table using psql
# 
# Next Steps:
#  Connect R to Postgres and bring the data into R for manipulation.

```{r}
library(DBI)

# using R-Postgres
con <- dbConnect(drv = RPostgres::Postgres(),
                 host = "localhost", 
                 dbname = "postgres", 
                 port = "5432", 
                 user = "postgres",
                 password = "aarshepicindia")

dbListTables(con)
dbWriteTable(con, "mtcars", mtcars)
dbListTables(con)

foo <- dbListFields(con, "mtcars")
foo

foo1 <- dbReadTable(con, "mtcars")
foo1

# using dplyr

con <- DBI::dbConnect(RPostgreSQL::PostgreSQL(), 
                      host = "localhost", 
                      user = "postgres", 
                      password = "aarshepicindia")

copy_to(con, nycflights13::flights, "flights",
  temporary = FALSE, 
  indexes = list(
    c("year", "month", "day"), 
    "carrier", 
    "tailnum",
    "dest"
  )
)



```

## Task 4: Extract broad areas from the list of addresses in the petrol pumps sheet


# Generating the focus areas list, from which each address will be looked up on Google
Maps to determine the best central area possible for that address.

```{r eval=FALSE, include=FALSE}
petrol_pumps_data <- read_csv("C:/Users/Hp/OneDrive/Desktop/EPICIndia/data-raw/smallTasksRmdScript-Task(ExtractBroadAreasFromListOfAddresses)/pmu_ws_CDVs_petrol_pumps_addresses.csv")

pincode_list_delhi <- read_csv("C:/Users/Hp/OneDrive/Desktop/EPICIndia/data-raw/smallTasksRmdScript-Task(ExtractBroadAreasFromListOfAddresses)/pin_code_list_delhi.csv")

# Number of unique addresses in the petrol pumps addresses dataset
num_unique_addresses <- length(unique(petrol_pumps_data$Address)) # 370

# Number of unique addresses that have a missing petrol pump name
foo <- petrol_pumps_data %>% filter(is.na(`Center Name`))
length(unique(foo$Address))

num_unique_addresses_miss_pp_name <- 


# clean petrol pumps addresses data

petrol_pump_addresses <- petrol_pumps_data %>%
  clean_names() %>%
  mutate(s_no = 1:nrow(petrol_pumps_data)) %>%
  select(s_no, center_name, address) %>%
  mutate(pincode = str_extract(address, "(-\\d{6})|(- \\d{6})")) %>%
  mutate(pincode = str_extract(pincode, "\\d+")) %>%
  arrange()

petrol_pump_addresses$pincode <- as.factor(petrol_pump_addresses$pincode)
petrol_pump_addresses_arranged <- arrange(petrol_pump_addresses, pincode)

write.csv(petrol_pump_addresses_arranged, "petrol_pump_addresses_arranged.csv")

# clean pin-code list data
pincode_list_delhi <- pincode_list_delhi %>%
  clean_names()

pincode_list_delhi$pincode <- as.factor(pincode_list_delhi$pincode)

# View(pincode_list_delhi)
# View(petrol_pump_addresses)


# sanity checks

length(unique(petrol_pump_addresses$pincode)) # 77 A pincode can represent more than one area.

sum(petrol_pump_addresses$pincode %in% pincode_list_delhi$Pincode) == length(petrol_pump_addresses$pincode)

sum(pincode_list_delhi$pincode %in% petrol_pump_addresses$pincode)
length(unique(pincode_list_delhi$pincode)) #95

# join above 2 datasets by pincode
master_pp_addresses_data <- left_join(petrol_pump_addresses, pincode_list_delhi, by = "pincode")

# clean master data

master_pp_addresses_data <- master_pp_addresses_data %>%
  clean_names() %>%
  select(-serial_no, -taluk) 

master_pp_addresses_data <- master_pp_addresses_data %>%
  arrange(pincode)

# pincodes_area_count <- count(master_pp_addresses_data, pincode)
# pincodes_area_count <- pincodes_area_count %>%
#   arrange(n)
# View(pincodes_area_count)

# Number of possible areas around which our petrol pumps are located
focus_areas <- count(master_pp_addresses_data, pincode, area)
focus_areas <- focus_areas %>%
  select(-n)

focus_areas <- focus_areas %>%
  arrange(pincode)

# Count of areas represented by each pincode
areas_rep_by_pincodes <- count(focus_areas, pincode)
areas_rep_by_pincodes <- areas_rep_by_pincodes %>%
  arrange(n)

View(areas_rep_by_pincodes)


# as.character(unique(master_pp_addresses_data$pincode))
# 
# 
# # sanity checks
# length(unique(master_pp_addresses_data$area)) # 481
# View(as.data.frame(unique(master_pp_addresses_data$area)))
# length(unique(master_pp_addresses_data$pincode)) # 77
# 
# # View(master_pp_addresses_data)
# 
# # locations out of which 30 broad areas need to be chosen
# 
# # areas_master_df <- as.data.frame(unique(master_pp_addresses_data$area))
# # areas_master_df <- as_tibble(areas_master_df)
# # colnames(areas_master_df)[1] <- "areas"
# 
# # count unique combinations of pincode and area
# count_pincode_area <- count(master_pp_addresses_data, pincode, area)
# View(count_pincode_area)
# 
# length(unique(count_pincode_area$pincode)) #77 unique pin codes.
# 
# 
# areas_master_df <- areas_master_df %>% arrange(areas)
# 
# View(areas_master_df)

write.csv(focus_areas, "focus_areas.csv")

```

# Generating a the petrol pump names list for SCTO choices sheet

```{r}

scto_choices_list_uids <- readxl::read_xlsx("./data-raw/smallTasksRmdScript-Task(ExtractBroadAreasFromListOfAddresses)/focus_areas_scto_list.xlsx", sheet = "uid_central_areas")

scto_addresses_df <- readxl::read_xlsx("./data-raw/smallTasksRmdScript-Task(ExtractBroadAreasFromListOfAddresses)/focus_areas_scto_list.xlsx", sheet = "addresses_central_areas")

scto_master_df <- left_join(scto_addresses_df, scto_choices_list_uids, by = "Location")

scto_master_df_arr_location <- scto_master_df %>% 
  arrange(uid_central_area)

scto_master_df_arr_by_grp <- scto_master_df %>%
  group_by(uid_central_area) %>%
  arrange(`Center Name`, .by_group = TRUE) %>%
  ungroup()


scto_master_df_arr_by_grp_exp_sheet <- scto_master_df_arr_by_grp %>%
  select(`Center Name`, uid_central_area)
  
  write_csv(scto_master_df_arr_by_grp_exp_sheet, "./output/smallTasksRmdScriptOutputFiles/smallTasksRmdScript-Task(ExtractBroadAreasFromListOfAddresses)/data_to_be_entered_into_scto_choices.csv")


View(scto_master_df_arr_by_grp)

View(select(filter(scto_master_df_arr_by_grp, uid_central_area == "anandvihar_ed"), 
            `Center Name`, uid_central_area, everything()))

```


# Checking for NA's in column wise unique values (for each of the 5 master tables) list for those columns of each table, that are too big to be opened in Excel.

```{r}

current_file_path <- c("./output/puccRawDataDumpDataCleaningRmdScriptOutputFiles/col_wise_unique_vals_in_five_master_tables/t_4_new_unique_values/t_4_new_vehicle_pucc_valid_upto.csv")

current_file <- read_csv(current_file_path)

# checks
sum(is.na(current_file$t_4_new_vehicle_pucc_valid_upto), na.rm = TRUE)
sum(is.null(current_file$t_4_new_vehicle_pucc_valid_upto), na.rm = TRUE)
sum(is.nan(current_file$t_4_new_vehicle_pucc_valid_upto), na.rm = TRUE)
sum(current_file$t_4_new_vehicle_pucc_valid_upto == "", na.rm = TRUE)
sum(current_file$t_4_new_vehicle_pucc_valid_upto == " ", na.rm = TRUE)
sum(current_file$t_4_new_vehicle_pucc_valid_upto == "-", na.rm = TRUE)
sum(current_file$t_4_new_vehicle_pucc_valid_upto == "--", na.rm = TRUE)

```

